---
title: "2016 California Contributors plots"
author: "Tianen Yao"
date: "2020-10-18"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    number_sections: yes
    toc: yes
    toc_float: yes
    code_folding: show
---


```{r, setup, echo=FALSE}
knitr::opts_chunk$set(
  message = FALSE, 
  warning = FALSE, 
  tidy=FALSE,     # display code as typed
  size="small")   # slightly smaller font for code
options(digits = 3)

# default figure size
knitr::opts_chunk$set(
  fig.width=6.75, 
  fig.height=6.75,
  fig.align = "center"
)
```


```{r load-libraries, warning=FALSE, message=FALSE, echo=FALSE}
library(tidyverse)  # Load ggplot2, dplyr, and all the other tidyverse packages
library(mosaic)
library(ggthemes)
library(lubridate)
library(fivethirtyeight)
library(here)
library(skimr)
library(janitor)
library(vroom)
library(tidyquant)
library(rvest)    # scrape websites
library(purrr)  
library(lubridate) #to handle dates
library(ggrepel)
library(tidytext)
```



2016 California Contributors plots

We would like make a plot that shows the top ten cities in highest amounts raised in political contributions in California during the 2016 US Presidential election.
Also, we would like to create the same plot for the top 10 candidates.


To get this plot, we shall join two dataframes; one contains all contributions, and another can translate zipcodes to cities.


```{r load_CA_data, warnings= FALSE, message=FALSE}

CA_contributors_2016 <- vroom::vroom(here::here("data","CA_contributors_2016.csv"))
zip_code_database <- vroom::vroom(here::here("data","zip_code_database.csv"))
zip_code_database_short <- zip_code_database[,c(1,3)]
#Left Join
CA_contributors_2016_with_St <-merge(x=CA_contributors_2016,y=zip_code_database_short,by="zip",all.x=TRUE)
#reorder with the primary_city based on raised_money
CA_contributors_2016_grouped <- CA_contributors_2016_with_St %>% 
  group_by(cand_nm, primary_city) %>%
  filter(cand_nm %in% c("Clinton, Hillary Rodham","Trump, Donald J.")) %>% 
  summarise(raised_money = sum(contb_receipt_amt)) %>% 
  arrange(desc(raised_money)) %>% 
  top_n(10) %>% 
  mutate(primary_city = reorder_within(primary_city, raised_money,cand_nm))
#make the plot for the two candidates
CA_contributors_2016_grouped %>% 
  ggplot(aes(primary_city,raised_money,fill = cand_nm)) +
  geom_col(show.legend = FALSE) +
    facet_wrap(~cand_nm, scales = "free", shrink=TRUE) +
    coord_flip() +
  scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Amount raised",
         x = NULL,
         title = "Where did the two candidates raise most money?") +
   theme(plot.title = element_text(size=20))
         axis.title.x = element_text(size=18, face="bold", margin=margin(20,0,0,0))
```

```{r top_ten_candidates,warnings= FALSE,message = FALSE, fig.width=15,fig.height=15}
top_ten_candidates <- CA_contributors_2016_with_St %>%  
  group_by(cand_nm) %>% 
  summarise(total_contribution=sum(contb_receipt_amt)) %>% 
  arrange(desc(total_contribution)) %>% top_n(10) %>% pull(1)

CA_top_ten_contributors_2016_grouped <- CA_contributors_2016_with_St %>% 
  group_by(cand_nm, primary_city) %>%
  filter(cand_nm %in% top_ten_candidates) %>% 
  summarise(raised_money = sum(contb_receipt_amt)) %>% 
  arrange(desc(raised_money)) %>% 
  top_n(10) %>% 
  mutate(primary_city = reorder_within(primary_city, raised_money,cand_nm))

CA_top_ten_contributors_2016_grouped$cand_nm <-factor(CA_top_ten_contributors_2016_grouped$cand_nm,levels=top_ten_candidates)

ggplot(CA_top_ten_contributors_2016_grouped,aes(primary_city,raised_money,fill = cand_nm)) +
  geom_col(show.legend = FALSE) +
    facet_wrap(~cand_nm, scales = "free",shrink=TRUE) +
    coord_flip() +
  scale_x_reordered() +
    scale_y_continuous(expand = c(0,0)) +
    labs(y = "Amount raised",
         x = NULL,
         title = "Where did top 10 candidates raise most money?"
         ) + theme(axis.text.x = element_text(size = 10),
        axis.text.y = element_text(size = 12),
        plot.title = element_text(size=40),
        strip.text.x = element_text(size = 12)
        )
```

